\textbf{The Illusion Game: A Novel Experimental Paradigm to study Visual Illusions}

### 2022-08-31 manuscript.Rmd
Update manuscript.Rmd

In line with our full open-access standards, all the material (stimuli generation code, experiment code, raw data, analysis script with complementary figures and analyses, preregistration, etc.) is available at **https://github.com/RealityBending/IllusionGameValidation**.

>>>>

In line with our open-science standards, all the material (stimuli generation code, experiment code, raw data, analysis script with complementary figures and analyses, preregistration, etc.) is available and open-source at **https://github.com/RealityBending/IllusionGameValidation**.
